Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2017-10-31 hpmoon-coor.tex
Modified title
Addressing reviewers suggestions

\title{Parallel multi-objective optimization using selective operator application
  islands}
% New title suggestion
% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
% PABLO: Renaming again to avoid using the co-evolutionary and
% cooperative
% Ok - JJ

@@

We have chosen those metrics because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}.

@@

ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely used in this area \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. The optimal PF distribution used for comparison has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. We have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time.
 The whole parameter set is summarized in Table \ref{tab:parameters}.

@@

The ECJ framework \citep{ECJ} has been used to run the
experiments. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
%\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
The
island model has been executed asynchronously, using the ECJ distributed inter-population exchange
 model, in a cluster of 16 nodes, each one with 16 Intel(R) Xeon(R) CPU E5520
@2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80. Islands have been first distributed among the nodes. That means that, for example, running with 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.

@@

Different metrics, previously explained, have been used
to calculate the quality of the obtained PFs in each configuration. As
some of the metrics  (such as HV) require a reference point to be
calculated, the point (1,9) has been chosen as reference, as none of
the generated PFs in all runs are dominated by it. Metrics are then
normalized with respect to that point. A Kruskal-Wallis significance
test has been performed to the metrics of all runs of the
configurations, as the Kolmogorov-Smirnov test detected non-normal
distributions. The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained with D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv.} in tables.

@@

8	&	0.900		&	0.816		& \textbf{	0.926	}		&	Equiv. D			& \textbf{	0.729	}	&	1.041			&	0.898			&	Equiv. D			&	0.013		&	0.029		& \textbf{	0.007	}	&	Equiv. D					\\
16	& \textbf{	0.880	}	&	0.675		&	0.839			&	Equiv. O			& \textbf{	0.721	}	&	0.897			&	0.983		D	&	Equiv. O			& \textbf{	0.017	}	&	0.062		&	0.025		&	Equiv. O					\\

@@

8	&	0.830		&	0.786		& \textbf{	0.851	}		&	Equiv. D			& \textbf{	0.866	}	&	0.996			&	0.987		D	&	Equiv. D			&	0.023		&	0.037		& \textbf{	0.017	}	&	Equiv. D					\\
16	& \textbf{	0.810	}	&	0.601		&	0.776			&	Equiv. O			& \textbf{	0.916	}	&	0.990			&	1.005		D	&	Equiv. O			& \textbf{	0.029	}	&	0.091		&	0.040		&	Equiv. O					\\

@@

8	&	0.928		&	0.838		& \textbf{	0.951	}		&	Equiv. D			& \textbf{	0.869	}	&	1.028			&	0.983		D	&	Equiv. D			& \textbf{	0.008	}	&	0.018		&	0.005		&	Equiv. D					\\
16	& \textbf{	0.903	}	&	0.715		&	0.870			&	Equiv. O			& \textbf{	0.846	}	&	0.899			&	0.960			&	Equiv. O			& \textbf{	0.011	}	&	0.032		&	0.014		&	Equiv. O					\\

@@

8	&	0.268		&	0.223		& \textbf{	0.298	}		&	Equiv. D			& \textbf{	0.988	}	& \textbf{	0.972	}	B	& \textbf{	0.996	}	B	&	Equiv. D			& \textbf{	0.173	}	&	0.191		&	0.160		&	Equiv. D					\\
16	& \textbf{	0.243	}	&	0.113		&	0.219			&	Equiv. O			& \textbf{	0.995	}	& \textbf{	0.987	}	B	& \textbf{	0.987	}	BD	&	Equiv. O			& \textbf{	0.184	}	&	0.240		&	0.193		&	Equiv. O					\\

@@

8	&	0.891		& \textbf{	0.953	}	&	0.937			&	Equiv. D			& \textbf{	0.681	}	& \textbf{	0.635	}	B	&	0.661		D	&	Equiv. D			&	0.015		& \textbf{	0.002	}	&	0.005		&	Equiv. D					\\
16	&	0.884		&	0.850		& \textbf{	0.942	}		&	Equiv. O			& \textbf{	0.705	}	&	0.908			& \textbf{	0.670	}	B	&	Equiv. O			&	0.016		&	0.022		& \textbf{	0.004	}	&	Equiv. O					\\

@@

8	&	0.832		& \textbf{	0.895	}	&	0.869			&	Equiv. D			& \textbf{	0.849	}	& \textbf{	0.886	}	B	&	0.853		D	&	Equiv. D			&	0.023		& \textbf{	0.006	}	&	0.013		&	Equiv. D					\\
16	&	0.831		&	0.833	B	& \textbf{	0.884	}		&	Equiv. O			& \textbf{	0.810	}	&	1.001			& \textbf{	0.802	}	B	&	Equiv. O			&	0.023		&	0.022	B	& \textbf{	0.009	}	&	Equiv. O					\\

@@

8	&	0.917		& \textbf{	0.971	}	&	0.960			&	Equiv. D			& \textbf{	0.843	}	& \textbf{	0.854	}	B	&	0.868		D	&	Equiv. D			&	0.009		& \textbf{	0.001	}	&	0.004		&	Equiv. D					\\
16	&	0.911		&	0.876	B	& \textbf{	0.963	}		&	Equiv. O			& \textbf{	0.864	}	&	0.899		B	& \textbf{	0.837	}	B	&	Equiv. O			&	0.010		&	0.014		& \textbf{	0.003	}	&	Equiv. O					\\

@@

8	&	0.271		& \textbf{	0.398	}	&	0.323			&	Equiv. D			& \textbf{	0.982	}	& \textbf{	0.982	}	B	&	0.994			&	Equiv. D			&	0.171		& \textbf{	0.115	}	&	0.149		&	Equiv. D					\\
16	&	0.275		&	0.295	B	& \textbf{	0.354	}		&	Equiv. O			& \textbf{	0.981	}	& \textbf{	0.970	}	B	&	1.006			&	Equiv. O			&	0.170		&	0.161	B	& \textbf{	0.136	}	&	Equiv. O					\\

@@

\begin{table*}
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per island}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline

\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																				\\ \hline
8	&	182.700		&	128.500		&	158.167			&	Equiv. D			&	397.367		&	776.967			&	603.667			&	Equiv. D				\\
16	&	132.567		&	43.633		&	76.167			&	Equiv. O			&	567.933		&	908.467			&	838.000			&	Equiv. O				\\
32	&	102.200		&	37.533		&	34.133	D		&	52.033			&	731.067		&	959.067			&	938.167			&	917.000				\\
64	&	81.100		&	46.267		&	26.300			&	30.167		O	&	846.733		&	978.733			&	972.567			&	927.133	B			\\
128	&	77.167		&	57.767		&	35.767			&	29.167		O	&	923.133		&	984.767			&	984.233	D		&	967.933				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	122.700		&	91.633		&	108.833	BD		&	Equiv. D			&	398.167		&	772.000			&	605.100			&	Equiv. D				\\
16	&	94.867		&	28.033		&	62.467			&	Equiv. O			&	574.567		&	908.433			&	840.900			&	Equiv. O				\\
32	&	56.633		&	11.433		&	19.467	D		&	31.567			&	735.867		&	960.167			&	939.200			&	904.900				\\
64	&	33.467		&	10.267		&	9.367	D		&	19.067			&	849.900		&	978.600			&	972.167			&	929.800	B			\\
128	&	22.833		&	12.633		&	7.800			&	13.967		D	&	929.433		&	984.567			&	984.233	D		&	971.700				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	212.900		&	129.233		&	171.367			&	Equiv. D			&	398.633		&	776.000			&	603.333			&	Equiv. D				\\
16	&	176.133		&	43.567		&	90.100			&	Equiv. O			&	573.033		&	908.667			&	838.000			&	Equiv. O				\\
32	&	121.500		&	42.800		&	33.200			&	56.900			&	733.233		&	959.000			&	937.967			&	918.833				\\
64	&	96.500		&	54.267		&	34.900			&	37.800		O	&	849.200		&	977.167			&	972.200			&	933.167				\\
128	&	76.700		&	62.200		&	41.767			&	33.867		D	&	924.000		&	984.733			&	984.367	D		&	966.433				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	42.233		&	28.633		&	35.967	BD		&	Equiv. D			&	396.900		&	773.400			&	603.533			&	Equiv. D				\\
16	&	43.733		&	7.733		&	18.967			&	Equiv. O			&	568.200		&	908.900			&	836.033			&	Equiv. O				\\
32	&	35.533		&	8.033		&	8.633	D		&	16.233		DO	&	735.700		&	958.900			&	938.600			&	926.167				\\
64	&	22.600		&	10.700		&	7.500	D		&	7.533		DO	&	850.267		&	978.067			&	972.467			&	940.267				\\
128	&	18.133		&	15.000	B	&	9.067			&	11.367		D	&	927.233		&	984.667			&	983.933	D		&	969.433				\\ \hline
\end{tabular}
}
\caption{Average number of generations and average number of solutions per island, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
\label{tab:sols512}
\end{table*}

\begin{table*}
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per island}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
%\multicolumn{13}{|c|}{2048 dimensions}																															\\ \hline
\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																					\\ \hline
8	&	137.733		&	47.167		&	119.933	B		&	Equiv. D			&	175.067		&	225.667			&	207.933			&	Equiv. D				\\
16	&	92.633		&	38.233		&	47.533	D		&	Equiv. O			&	204.867		&	238.533			&	232.900			&	Equiv. O				\\
32	&	56.167		&	41.167		&	28.667			&	32.567	O		&	225.433		&	243.833			&	242.533			&	242.000	O			\\
64	&	50.900		&	49.667	B	&	35.600			&	25.367			&	236.500		&	245.967			&	245.700			&	244.033	D			\\
128	&	45.767		&	64.933		&	44.167	B		&	31.867			&	242.800		&	247.000			&	247.000	D		&	245.733				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	64.267		&	22.733		&	56.867	B		&	Equiv. D			&	175.633		&	226.000			&	208.100			&	Equiv. D				\\
16	&	52.300		&	10.733		&	20.067	D		&	Equiv. O			&	205.033		&	238.867			&	233.100			&	Equiv. O				\\
32	&	34.400		&	10.367		&	10.433	D		&	17.900	O		&	225.600		&	244.267			&	242.633			&	242.000	O			\\
64	&	24.600		&	10.900		&	9.267	D		&	12.867	DO		&	236.700		&	246.000			&	245.767			&	244.033	D			\\
128	&	18.667		&	17.833	B	&	10.367			&	12.933	O		&	243.367		&	247.000			&	247.000	d		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	163.767		&	83.367		&	119.467			&	Equiv. D			&	176.533		&	226.400			&	207.700			&	Equiv. D				\\
16	&	108.467		&	49.433		&	47.700	D		&	Equiv. O			&	205.333		&	238.467			&	232.933			&	Equiv. O				\\
32	&	72.133		&	44.333		&	31.833			&	36.533	O		&	225.100		&	243.900			&	242.433			&	242.000	O			\\
64	&	54.867		&	57.600	B	&	40.633			&	29.300			&	236.333		&	245.933			&	245.733			&	244.000	D			\\
128	&	50.600		&	72.133		&	49.033	B		&	34.933			&	243.200		&	247.000			&	247.000	D		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	22.133		&	13.833		&	14.433	D		&	Equiv. D			&	175.733		&	226.100			&	207.767			&	Equiv. D				\\
16	&	20.767		&	15.867		&	13.300	D		&	Equiv. O			&	205.033		&	238.433			&	232.933			&	Equiv. O				\\
32	&	22.600		&	10.700		&	10.033	D		&	11.967	DO		&	225.833		&	243.667			&	242.500			&	242.000	O			\\
64	&	19.033		&	11.267		&	10.533	D		&	10.567	DO		&	236.433		&	245.900			&	245.833			&	244.000	D			\\
128	&	15.800		&	24.500		&	11.600			&	12.233	DO		&	243.800		&	247.000			&	247.000	D		&	245.533				\\ \hline
\end{tabular}
}
\caption{Average number of generations and average number of solutions per island, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
\label{tab:sols2048}
\end{table*}

@@

%EXPLANATION OF THE RESULTS
This can be explained comparing the number of non-dominated solutions
in each island and the average number of generations (Table
\ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
lengths, increasing the number of islands implies more generations
with all the methods (logically, as there are less individuals in each
island). But also, the SLA methods
approach to the number of generations with the baseline when
increasing the number of islands. However, with $L=2048$ the migration
time is big enough  to not improve the number of generations
with respect to the baseline, even in the lower number of islands, as
it happens with $L=512$. Therefore, more generations do not
necessarily improve the solution of the global PF, but focusing on
different elements of the chromosome. As  previously stated, every
island is unaware of the other islands PFs, and they are trying to
optimize their solutions independently. With respect to the average
number of solutions in each island, there is a clear difference 
 with the baseline with $L=512$, where this value is in the most
of the cases, less than a half. The number of non-dominated solutions
also implies a better Spread indicator, where the baseline 
 obtains better (or not significantly different) values in the majority of the compared configurations. %TENGO QUE COMENTAR MAS LOS RESULTADOS Y
                              %ENTENDERLO TODO Y JUSTIFICARLO
                              %FINAMENTE
%Almost always no es muy preciso - JJ Pablo: arreglao

>>>>

\title{Distributed multi-objective evolutionary optimization using island-based selective operator application}
% New title suggestion
% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
% PABLO: Renaming again to avoid using the co-evolutionary and
% cooperative
% Ok - JJ

@@

We have chosen those metrics because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}. Mathematical formulation of these metrics can be seen in \cite{Dorronsoro13superlinear}.

@@

ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the most widely used in this area \citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This benchmark includes several functions, with different features that are representative of real world optimization problems. Mathematical formulation of each function is available in \citep{zdt2000a}.  The optimal PF distribution used for comparison has 1000 solutions \footnote{Optimal PFs are available at:   \url{http://www.tik.ee.ethz.ch/sop/download/supplementary/testproblems/}.}.

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}.
 The whole parameter set is summarized in Table \ref{tab:parameters}.

@@

The ECJ framework \citep{ECJ} has been used to run the
experiments, including its own random number generation implementation. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
%\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
The
island model has been executed asynchronously, using the ECJ distributed inter-population exchange
 model, in a cluster of 16 nodes, each one with 16 Intel(R) Xeon(R) CPU E5520
@2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80. Islands have been first distributed among the nodes. That means that, for example, running with 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.

@@

Different metrics, previously explained, have been used
to calculate the quality of the obtained PFs in each configuration. As
some of the metrics  (such as HV) require a reference point to be
calculated, the point (1,9) has been chosen as reference, as none of
the generated PFs in all runs are dominated by it. Metrics are then
normalized with respect to that point. A Kruskal-Wallis significance
test has been performed to the metrics of all runs of the
configurations, as the Kolmogorov-Smirnov test detected non-normal
distributions. The average results for each configuration are shown in
Table \ref{tab:results512} (for 512 dimensions) and
\ref{tab:results2048} (for 2048). As previously explained, when $P=8$
the results of A are equivalent to the obtained with D (because
$c=0$), and when $P=16$ they are equivalent to O ($c=1$). We refer this equivalence with the word {\em Equiv-} in tables. For example, Equiv-D in an HV cell  means that the HV of A is the same than the one in D column, because the behaviour of this configuration is the same than executing D.

@@

8	&	0.900		&	0.816		& \textbf{	0.926	}		&	Equiv-D			& \textbf{	0.729	}	&	1.041			&	0.898			&	Equiv-D			&	0.013		&	0.029		& \textbf{	0.007	}	&	Equiv-D					\\
16	& \textbf{	0.880	}	&	0.675		&	0.839			&	Equiv-O			& \textbf{	0.721	}	&	0.897			&	0.983		D	&	Equiv-O			& \textbf{	0.017	}	&	0.062		&	0.025		&	Equiv-O					\\

@@

8	&	0.830		&	0.786		& \textbf{	0.851	}		&	Equiv-D			& \textbf{	0.866	}	&	0.996			&	0.987		D	&	Equiv-D			&	0.023		&	0.037		& \textbf{	0.017	}	&	Equiv-D					\\
16	& \textbf{	0.810	}	&	0.601		&	0.776			&	Equiv-O			& \textbf{	0.916	}	&	0.990			&	1.005		D	&	Equiv-O			& \textbf{	0.029	}	&	0.091		&	0.040		&	Equiv-O					\\

@@

8	&	0.928		&	0.838		& \textbf{	0.951	}		&	Equiv-D			& \textbf{	0.869	}	&	1.028			&	0.983		D	&	Equiv-D			& \textbf{	0.008	}	&	0.018		&	0.005		&	Equiv-D					\\
16	& \textbf{	0.903	}	&	0.715		&	0.870			&	Equiv-O			& \textbf{	0.846	}	&	0.899			&	0.960			&	Equiv-O			& \textbf{	0.011	}	&	0.032		&	0.014		&	Equiv-O					\\

@@

8	&	0.268		&	0.223		& \textbf{	0.298	}		&	Equiv-D			& \textbf{	0.988	}	& \textbf{	0.972	}	B	& \textbf{	0.996	}	B	&	Equiv-D			& \textbf{	0.173	}	&	0.191		&	0.160		&	Equiv-D					\\
16	& \textbf{	0.243	}	&	0.113		&	0.219			&	Equiv-O			& \textbf{	0.995	}	& \textbf{	0.987	}	B	& \textbf{	0.987	}	BD	&	Equiv-O			& \textbf{	0.184	}	&	0.240		&	0.193		&	Equiv-O					\\

@@

8	&	0.891		& \textbf{	0.953	}	&	0.937			&	Equiv-D			& \textbf{	0.681	}	& \textbf{	0.635	}	B	&	0.661		D	&	Equiv-D			&	0.015		& \textbf{	0.002	}	&	0.005		&	Equiv-D					\\
16	&	0.884		&	0.850		& \textbf{	0.942	}		&	Equiv-O			& \textbf{	0.705	}	&	0.908			& \textbf{	0.670	}	B	&	Equiv-O			&	0.016		&	0.022		& \textbf{	0.004	}	&	Equiv-O					\\

@@

8	&	0.832		& \textbf{	0.895	}	&	0.869			&	Equiv-D			& \textbf{	0.849	}	& \textbf{	0.886	}	B	&	0.853		D	&	Equiv-D			&	0.023		& \textbf{	0.006	}	&	0.013		&	Equiv-D					\\
16	&	0.831		&	0.833	B	& \textbf{	0.884	}		&	Equiv-O			& \textbf{	0.810	}	&	1.001			& \textbf{	0.802	}	B	&	Equiv-O			&	0.023		&	0.022	B	& \textbf{	0.009	}	&	Equiv-O					\\

@@

8	&	0.917		& \textbf{	0.971	}	&	0.960			&	Equiv-D			& \textbf{	0.843	}	& \textbf{	0.854	}	B	&	0.868		D	&	Equiv-D			&	0.009		& \textbf{	0.001	}	&	0.004		&	Equiv-D					\\
16	&	0.911		&	0.876	B	& \textbf{	0.963	}		&	Equiv-O			& \textbf{	0.864	}	&	0.899		B	& \textbf{	0.837	}	B	&	Equiv-O			&	0.010		&	0.014		& \textbf{	0.003	}	&	Equiv-O					\\

@@

8	&	0.271		& \textbf{	0.398	}	&	0.323			&	Equiv-D			& \textbf{	0.982	}	& \textbf{	0.982	}	B	&	0.994			&	Equiv-D			&	0.171		& \textbf{	0.115	}	&	0.149		&	Equiv-D					\\
16	&	0.275		&	0.295	B	& \textbf{	0.354	}		&	Equiv-O			& \textbf{	0.981	}	& \textbf{	0.970	}	B	&	1.006			&	Equiv-O			&	0.170		&	0.161	B	& \textbf{	0.136	}	&	Equiv-O					\\

@@

\begin{table*}
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline

\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																				\\ \hline
8	&	182.700		&	128.500		&	158.167			&	Equiv-D			&	397.367		&	776.967			&	603.667			&	Equiv-D				\\
16	&	132.567		&	43.633		&	76.167			&	Equiv-O			&	567.933		&	908.467			&	838.000			&	Equiv-O				\\
32	&	102.200		&	37.533		&	34.133	D		&	52.033			&	731.067		&	959.067			&	938.167			&	917.000				\\
64	&	81.100		&	46.267		&	26.300			&	30.167		O	&	846.733		&	978.733			&	972.567			&	927.133	B			\\
128	&	77.167		&	57.767		&	35.767			&	29.167		O	&	923.133		&	984.767			&	984.233	D		&	967.933				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	122.700		&	91.633		&	108.833	BD		&	Equiv-D			&	398.167		&	772.000			&	605.100			&	Equiv-D				\\
16	&	94.867		&	28.033		&	62.467			&	Equiv-O			&	574.567		&	908.433			&	840.900			&	Equiv-O				\\
32	&	56.633		&	11.433		&	19.467	D		&	31.567			&	735.867		&	960.167			&	939.200			&	904.900				\\
64	&	33.467		&	10.267		&	9.367	D		&	19.067			&	849.900		&	978.600			&	972.167			&	929.800	B			\\
128	&	22.833		&	12.633		&	7.800			&	13.967		D	&	929.433		&	984.567			&	984.233	D		&	971.700				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	212.900		&	129.233		&	171.367			&	Equiv-D			&	398.633		&	776.000			&	603.333			&	Equiv-D				\\
16	&	176.133		&	43.567		&	90.100			&	Equiv-O			&	573.033		&	908.667			&	838.000			&	Equiv-O				\\
32	&	121.500		&	42.800		&	33.200			&	56.900			&	733.233		&	959.000			&	937.967			&	918.833				\\
64	&	96.500		&	54.267		&	34.900			&	37.800		O	&	849.200		&	977.167			&	972.200			&	933.167				\\
128	&	76.700		&	62.200		&	41.767			&	33.867		D	&	924.000		&	984.733			&	984.367	D		&	966.433				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	42.233		&	28.633		&	35.967	BD		&	Equiv-D			&	396.900		&	773.400			&	603.533			&	Equiv-D				\\
16	&	43.733		&	7.733		&	18.967			&	Equiv-O			&	568.200		&	908.900			&	836.033			&	Equiv-O				\\
32	&	35.533		&	8.033		&	8.633	D		&	16.233		DO	&	735.700		&	958.900			&	938.600			&	926.167				\\
64	&	22.600		&	10.700		&	7.500	D		&	7.533		DO	&	850.267		&	978.067			&	972.467			&	940.267				\\
128	&	18.133		&	15.000	B	&	9.067			&	11.367		D	&	927.233		&	984.667			&	983.933	D		&	969.433				\\ \hline
\end{tabular}
}
\caption{Average number of generations and average number of solutions of the front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 512 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
\label{tab:sols512}
\end{table*}

\begin{table*}
\centering
\resizebox{12cm}{!}{
\begin{tabular}{|c||c|c|c|c||c|c|c|c||}
\hline
	&	\multicolumn{4}{|c|}{Average solutions per front}													&	\multicolumn{4}{|c|}{Generations}															\\ \hline
%\multicolumn{13}{|c|}{2048 dimensions}																															\\ \hline
\#Island	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A				\\ \hline
\multicolumn{9}{|c|}{ZDT1}																					\\ \hline
8	&	137.733		&	47.167		&	119.933	B		&	Equiv-D			&	175.067		&	225.667			&	207.933			&	Equiv-D				\\
16	&	92.633		&	38.233		&	47.533	D		&	Equiv-O			&	204.867		&	238.533			&	232.900			&	Equiv-O				\\
32	&	56.167		&	41.167		&	28.667			&	32.567	O		&	225.433		&	243.833			&	242.533			&	242.000	O			\\
64	&	50.900		&	49.667	B	&	35.600			&	25.367			&	236.500		&	245.967			&	245.700			&	244.033	D			\\
128	&	45.767		&	64.933		&	44.167	B		&	31.867			&	242.800		&	247.000			&	247.000	D		&	245.733				\\ \hline
\multicolumn{9}{|c|}{ZDT2}																															\\ \hline
8	&	64.267		&	22.733		&	56.867	B		&	Equiv-D			&	175.633		&	226.000			&	208.100			&	Equiv-D				\\
16	&	52.300		&	10.733		&	20.067	D		&	Equiv-O			&	205.033		&	238.867			&	233.100			&	Equiv-O				\\
32	&	34.400		&	10.367		&	10.433	D		&	17.900	O		&	225.600		&	244.267			&	242.633			&	242.000	O			\\
64	&	24.600		&	10.900		&	9.267	D		&	12.867	DO		&	236.700		&	246.000			&	245.767			&	244.033	D			\\
128	&	18.667		&	17.833	B	&	10.367			&	12.933	O		&	243.367		&	247.000			&	247.000	d		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT3}																															\\ \hline
8	&	163.767		&	83.367		&	119.467			&	Equiv-D			&	176.533		&	226.400			&	207.700			&	Equiv-D				\\
16	&	108.467		&	49.433		&	47.700	D		&	Equiv-O			&	205.333		&	238.467			&	232.933			&	Equiv-O				\\
32	&	72.133		&	44.333		&	31.833			&	36.533	O		&	225.100		&	243.900			&	242.433			&	242.000	O			\\
64	&	54.867		&	57.600	B	&	40.633			&	29.300			&	236.333		&	245.933			&	245.733			&	244.000	D			\\
128	&	50.600		&	72.133		&	49.033	B		&	34.933			&	243.200		&	247.000			&	247.000	D		&	245.833				\\ \hline
\multicolumn{9}{|c|}{ZDT6}																															\\ \hline
8	&	22.133		&	13.833		&	14.433	D		&	Equiv-D			&	175.733		&	226.100			&	207.767			&	Equiv-D				\\
16	&	20.767		&	15.867		&	13.300	D		&	Equiv-O			&	205.033		&	238.433			&	232.933			&	Equiv-O				\\
32	&	22.600		&	10.700		&	10.033	D		&	11.967	DO		&	225.833		&	243.667			&	242.500			&	242.000	O			\\
64	&	19.033		&	11.267		&	10.533	D		&	10.567	DO		&	236.433		&	245.900			&	245.833			&	244.000	D			\\
128	&	15.800		&	24.500		&	11.600			&	12.233	DO		&	243.800		&	247.000			&	247.000	D		&	245.533				\\ \hline
\end{tabular}
}
\caption{Average number of generations and average number of solutions per front, obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and adaptive overlapped (A), using a chromosome length of 2048 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value.}
\label{tab:sols2048}
\end{table*}

@@

%EXPLANATION OF THE RESULTS
This can be explained comparing the number of non-dominated solutions
of each front and the average number of generations (Table
\ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome
lengths, increasing the number of islands implies more generations
with all the methods (logically, as there are less individuals in each
island). But also, the SLA methods
approach to the number of generations with the baseline when
increasing the number of islands. However, with $L=2048$ the migration
time is big enough  to not improve the number of generations
with respect to the baseline, even in the lower number of islands, as
it happens with $L=512$. Therefore, more generations do not
necessarily improve the solution of the global PF, but focusing on
different elements of the chromosome. As  previously stated, every
island is unaware of the other islands PFs, and they are trying to
optimize their solutions independently. With respect to the average
number of solutions per front, there is a clear difference 
 with the baseline with $L=512$, where this value is in the most
of the cases, less than a half. The number of non-dominated solutions
also implies a better Spread indicator, where the baseline 
 obtains better (or not significantly different) values in the majority of the compared configurations. %TENGO QUE COMENTAR MAS LOS RESULTADOS Y
                              %ENTENDERLO TODO Y JUSTIFICARLO
                              %FINAMENTE
%Almost always no es muy preciso - JJ Pablo: arreglao
